Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/paper.tex
Use the colours everywhere

% pretty colours
\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
\definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}

@@

\begin{figure}[b] % first page if possible
    \centering
    \begin{tikzpicture}[scale=0.33]%{{{
        \begin{scope}[rotate=90]
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

@@

        \begin{scope}[xshift=7cm, rotate=90]
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

@@

        \begin{scope}[xshift=18cm, rotate=90]
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

@@

        \begin{scope}[xshift=25cm, rotate=90]
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

@@

        \begin{scope}[xshift=12.8cm]
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
            \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
            \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};

@@

            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (5.6, 0) {\phantom{0}};

@@

        \begin{scope}[xshift=25.6cm]
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
            \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};

@@

            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (5.6, 0) {\phantom{0}};

@@

        \begin{scope}[yshift=-9cm]
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
            \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
            \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};

@@

            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
            \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (5.6, 0) {\phantom{0}};

@@

        \begin{scope}[xshift=12.8cm, yshift=-9cm]
            \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
            \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};

@@

                    \node [anchor=west] (Vs) at (5.5, 3.5) { $\{ (a, 1) \}$ };
                    \node [anchor=west] (Vb) at (5.5, 2) { $\{ b, c, d \} \times \{1 \ldots 5 \}$ };
                    \node [anchor=west] (Vr) at (5.5, 0.5) { $(\{ b, c, d \} \times \{ 2, 3 \}) \cup (\{ e, f\} \times \{ 4, 5 \})$ };
            \end{tikzpicture}
            \\[0.1cm]
            \stepcounter{stepcounter2}\roman{stepcounter2}) Initial problem &
            \stepcounter{stepcounter2}\roman{stepcounter2}) Search variables after guessing $a \mapsto 1$
            \\[0.2cm]
            \begin{tikzpicture}[scale=0.33]
                    \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 2) {\phantom{0}};
                    \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 2) {\phantom{0}};
                    \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf4) at (0, 0) {\phantom{0}};
                    \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf5) at (3, 0) {\phantom{0}};

@@

                    \draw (Me4) -- (Mf5);
                    \draw (Me5) -- (Mf4);
            \end{tikzpicture}
            &
            \begin{tikzpicture}[scale=0.33]
                    \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb2) at (3, 2) {\phantom{0}};
                    \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb3) at (6, 2) {\phantom{0}};
                    \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc2) at (0, 0) {\phantom{0}};
                    \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc3) at (3, 0) {\phantom{0}};
                    \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md2) at (6, 0) {\phantom{0}};
                    \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 0) {\phantom{0}};

@@

                    \draw (Mb2) -- (Mc3);
                    \draw (Mb2) -- (Md3);
                    \draw (Mb3) -- (Mc2);
                    \draw (Mb3) -- (Md2);
            \end{tikzpicture}
            \\[0.1cm]
            \stepcounter{stepcounter2}\roman{stepcounter2}) $\mathit{remaining} \setminus \mathit{branchable}$ &
            \stepcounter{stepcounter2}\roman{stepcounter2}) $\mathit{remaining} \cap \mathit{branchable}$
            \\
        };
    \end{tikzpicture}\\[0.1cm]\begin{tikzpicture}[scale=0.33]
        \matrix (m) [matrix of nodes] {
            \begin{tikzpicture}[scale=0.33]
                \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 0) {\phantom{0}};
                \node[draw, circle, fill=uofgsunshine, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 0) {\phantom{0}};
                \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf4) at (6, 0) {\phantom{0}};
                \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mf5) at (9, 0) {\phantom{0}};
                \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb2) at (12, 0) {\phantom{0}};
                \node[draw, circle, fill=uofglawn, inner sep=0.5pt, font=\normalsize] (Mb3) at (15, 0) {\phantom{0}};
                \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc2) at (18, 0) {\phantom{0}};
                \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Mc3) at (21, 0) {\phantom{0}};
                \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md2) at (24, 0) {\phantom{0}};
                \node[draw, circle, fill=uofgthistle, inner sep=0.5pt, font=\normalsize] (Md3) at (27, 0) {\phantom{0}};

>>>>

% pretty colours
\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
\definecolor{chromayellow}{rgb}{1.0, 1.0, 0.878431}
\definecolor{chromagreen}{rgb}{0.564706, 0.933333, 0.564706}
\definecolor{chromateal}{rgb}{0, 0.501961, 0.501961}
\definecolor{chromanavy}{rgb}{0, 0, 0.501961}

@@

\begin{figure}[b] % first page if possible
    \centering
    \begin{tikzpicture}[scale=0.33]%{{{
        \begin{scope}[rotate=90]
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

@@

        \begin{scope}[xshift=7cm, rotate=90]
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

@@

        \begin{scope}[xshift=18cm, rotate=90]
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M8) at ($(330:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(270:1.5) + (M6)$) {\phantom{0}};

@@

        \begin{scope}[xshift=25cm, rotate=90]
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M1) at (90:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M2) at (150:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M3) at (30:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M4) at (210:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M5) at (330:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M6) at (270:1.5) {\phantom{0}};
            \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (M7) at ($(210:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M8) at ($(270:1.5) + (M6)$) {\phantom{0}};
            \node[draw, circle, draw=uofgsandstone!40, fill=white, inner sep=0.5pt, font=\normalsize] (M9) at ($(330:1.5) + (M8)$) {\phantom{0}};

@@

        \begin{scope}[xshift=12.8cm]
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
            \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
            \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};

@@

            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (5.6, 0) {\phantom{0}};

@@

        \begin{scope}[xshift=25.6cm]
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
            \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};

@@

            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (5.6, 0) {\phantom{0}};

@@

        \begin{scope}[yshift=-9cm]
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
            \node[draw, dotted, circle, fill=white, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};

@@

            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (M1) at (5.6, 4) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (M2) at (7.6, 4) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M3) at (5.6, 2) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (M4) at (7.6, 2) {\phantom{0}};
            \node[draw, circle, fill=white, inner sep=0.5pt, font=\normalsize] (M5) at (5.6, 0) {\phantom{0}};

@@

        \begin{scope}[xshift=12.8cm, yshift=-9cm]
            \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Ma) at (0, 4) {\phantom{0}};
            \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb) at (0, 2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc) at (2, 2) {\phantom{0}};
            \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md) at (0, 0) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Me) at (2, 0) {\phantom{0}};

@@

                    \node [anchor=west] (Vs) at (5.5, 3.5) { $\{ (a, 1) \}$ };
                    \node [anchor=west] (Vb) at (5.5, 2) { $\{ b, c, d \} \times \{1 \ldots 5 \}$ };
                    \node [anchor=west] (Vr) at (5.5, 0.5) { $(\{ b, c, d \} \times \{ 2, 3 \}) \cup (\{ e, f\} \times \{ 4, 5 \})$ };
            \end{tikzpicture}
            \\[0.1cm]
            \stepcounter{stepcounter2}\roman{stepcounter2}) Initial problem &
            \stepcounter{stepcounter2}\roman{stepcounter2}) Search variables after guessing $a \mapsto 1$
            \\[0.2cm]
            \begin{tikzpicture}[scale=0.33]
                    \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 2) {\phantom{0}};
                    \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 2) {\phantom{0}};
                    \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (Mf4) at (0, 0) {\phantom{0}};
                    \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (Mf5) at (3, 0) {\phantom{0}};

@@

                    \draw (Me4) -- (Mf5);
                    \draw (Me5) -- (Mf4);
            \end{tikzpicture}
            &
            \begin{tikzpicture}[scale=0.33]
                    \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb2) at (3, 2) {\phantom{0}};
                    \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb3) at (6, 2) {\phantom{0}};
                    \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Mc2) at (0, 0) {\phantom{0}};
                    \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Mc3) at (3, 0) {\phantom{0}};
                    \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md2) at (6, 0) {\phantom{0}};
                    \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 0) {\phantom{0}};

@@

                    \draw (Mb2) -- (Mc3);
                    \draw (Mb2) -- (Md3);
                    \draw (Mb3) -- (Mc2);
                    \draw (Mb3) -- (Md2);
            \end{tikzpicture}
            \\[0.1cm]
            \stepcounter{stepcounter2}\roman{stepcounter2}) $\mathit{remaining} \setminus \mathit{branchable}$ &
            \stepcounter{stepcounter2}\roman{stepcounter2}) $\mathit{remaining} \cap \mathit{branchable}$
            \\
        };
    \end{tikzpicture}\\[0.1cm]\begin{tikzpicture}[scale=0.33]
        \matrix (m) [matrix of nodes] {
            \begin{tikzpicture}[scale=0.33]
                \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Me4) at (0, 0) {\phantom{0}};
                \node[draw, circle, fill=chromayellow, inner sep=0.5pt, font=\normalsize] (Me5) at (3, 0) {\phantom{0}};
                \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (Mf4) at (6, 0) {\phantom{0}};
                \node[draw, circle, fill=chromateal, inner sep=0.5pt, font=\normalsize] (Mf5) at (9, 0) {\phantom{0}};
                \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb2) at (12, 0) {\phantom{0}};
                \node[draw, circle, fill=chromagreen, inner sep=0.5pt, font=\normalsize] (Mb3) at (15, 0) {\phantom{0}};
                \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Mc2) at (18, 0) {\phantom{0}};
                \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Mc3) at (21, 0) {\phantom{0}};
                \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md2) at (24, 0) {\phantom{0}};
                \node[draw, circle, fill=chromanavy, inner sep=0.5pt, font=\normalsize] (Md3) at (27, 0) {\phantom{0}};
